Lake Photic Zone Temperature accross the Conterminous United States

### 2019-06-06 manuscript/manuscript.Rmd
Building figures
adding figures to manuscript

```{r setup, include=FALSE, eval=FALSE}
source(here::here("R/functions.R"), encoding = "UTF-8")
opts_chunk$set(echo = TRUE, fig.width=6, fig.height=5)
tab_num <- captioner(prefix = "Table")
fig_num <- captioner(prefix = "Figure")
options(scipen = 2, digits = 5)
```

@@

>>>>

```{r setup, include=FALSE, eval=FALSE}
# source(here::here("R/functions.R"), encoding = "UTF-8")
library(captioner)
#opts_chunk$set(echo = TRUE, fig.width=6, fig.height=5)
tab_num <- captioner(prefix = "Table")
fig_num <- captioner(prefix = "Figure")
options(scipen = 2, digits = 5)

```

@@

![`r fig_num("varsel_fig",caption="Variable selection plot for all variables. Shows percent increase in mean‐squared error as a function of the number of variables.")`](../figures/varselfig.jpg)
